Figures

### 2020-02-28 manuscript/figures.Rmd
cleanup, fight with figure numbering

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{colortbl}
- \usepackage{float}
---

@@

![Summary of lake depth predictor variables.](../tables/01_predictors.pdf){width=65%}

@@

```{r depth_model_metrics, fig.cap = "depth model metrics", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../tables/depth_model_metrics-1.pdf")
```

@@

# Appendix

@@

```{r heatmap, fig.cap = "Correlation matrix heatmap.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_heatmap-1.pdf")
```

@@

```{r contrasts_tally, fig.cap = "Number of lake depth measurements by categories.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_contrasts_tally-1.pdf")
```

```{r 02_depth_model_fitted, fig.cap = "A model that does not include shape class over predicts depth in concave lakes but does not systematically under predict depth in convex lakes.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/02_depth_model_fitted-1.pdf")
```

```{r 02_depth_oliver-2, fig.cap = "Reproduction of Oliver 2016 using LAGOSUS data in LAGOSNE footprint.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/02_depth_oliver-2.pdf")
```

```{r 02_depth_oliver-1, fig.cap = "Reproduction of Oliver 2016 using LAGOSUS data in LAGOSNE footprint.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/02_depth_oliver-1.pdf")
```

```{r 02_depth_oliver-4, fig.cap = "Oliver 2016 observed versus predicted.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/02_depth_oliver-4.pdf")
```

@@

![Messager et al. 2016 equation table](../figures/messager_eq_table.png){width=100%}

>>>>

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{colortbl}
- \usepackage{float}
- \usepackage{caption}
---

@@

\captionsetup[figure]{name=Table}
\captionsetup[figure]{labelformat=empty}
```{r 01_predictors, fig.cap = "Table 1: Summary of lake depth predictor variables", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../tables/01_predictors.pdf")
```
\captionsetup[figure]{name=Figure}
\captionsetup[figure]{labelformat=default}
\setcounter{figure}{4}

@@

\captionsetup[figure]{name=Table}
\captionsetup[figure]{labelformat=empty}
```{r depth_model_metrics, fig.cap = "Table 2: depth model metrics", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../tables/depth_model_metrics-1.pdf")
```
\captionsetup[figure]{name=Figure}
\captionsetup[figure]{labelformat=default}
\setcounter{figure}{5}

@@

# Appendix
\setcounter{figure}{0}

@@

```{r heatmap, fig.cap = "Correlation matrix heatmap.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/slope-compare-1.pdf")
```

@@

```{r contrasts_tally, fig.cap = "Number of lake depth measurements by categories.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/01_contrasts_tally-1.pdf")
```

```{r 02_depth_model_fitted, fig.cap = "A model that does not include shape class over predicts depth in concave lakes but does not systematically under predict depth in convex lakes.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/02_depth_model_fitted-1.pdf")
```

```{r 02_depth_oliver-2, fig.cap = "Reproduction of Oliver 2016 using LAGOSUS data in LAGOSNE footprint.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/02_depth_oliver-2.pdf")
```

```{r 02_depth_oliver-1, fig.cap = "Reproduction of Oliver 2016 using LAGOSUS data in LAGOSNE footprint.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/02_depth_oliver-1.pdf")
```

```{r 02_depth_oliver-4, fig.cap = "Oliver 2016 observed versus predicted.", warning=FALSE, echo = FALSE, eval=FALSE}
knitr::include_graphics("../figures/02_depth_oliver-4.pdf")
```

@@

<!-- ![Messager et al. 2016 equation table](../figures/messager_eq_table.png){width=100%} -->
